Visual Inference for Goodness-of-Fit for A Network Model

### 2017-09-29 ASApaper/paper.Rmd
add simulated data

```{r M1, echo = FALSE, message=FALSE,warning=FALSE}
M1senateEsts <- read_csv("../Data/senate/basicModelFitsSenate1000.csv")
inisdSenateEsts <- read_csv("../Data/senate/inisdModelFitsSenate1000.csv")
jttpSenateEsts <- read_csv("../Data/senate/jttpModelFitsSenateAll1000.csv")
jttsSenateEsts <- read_csv("../Data/senate/jttsModelFitsSenateAll1000.csv")
# ggpairs(M1senateEsts, columns = 1:8)
# M1senateEsts %>% mutate(converged = (maxConv <= 0.25)) %>% 
#   ggplot() + 
#   geom_density(aes(x = density, color = converged), adjust = .5) 
# M1senateEsts %>% mutate(converged = (maxConv <= 0.25)) %>% 
#   ggplot() + 
#   geom_histogram(aes(x = density, color = converged), binwidth = .005, fill = NA) + facet_wrap(~converged)

# make ests long - M1
M1senateEsts %>% 
  select(Rate:recip, maxConv, sim) %>% 
  gather(parameter, estimate, Rate:recip) -> melt1 
M1senateEsts %>% 
  select(se_density:sim) %>% 
  gather(parameter, se, se_density:se_recip) %>% 
  mutate(parameter = str_replace(parameter, "se_", "")) -> melt2 
left_join(melt1, melt2) %>% arrange(sim) -> M1SenEstsLong

# make ests long - inisd
inisdSenateEsts %>% 
  select(Rate:inIsDegree, maxConv, sim) %>% 
  gather(parameter, estimate, Rate:inIsDegree) -> melt1 
inisdSenateEsts %>% 
  select(se_density:sim) %>% 
  gather(parameter, se, se_density:se_inIsDegree) %>% 
  mutate(parameter = str_replace(parameter, "se_", "")) -> melt2 
left_join(melt1, melt2) %>% arrange(sim) -> inisdSenEstsLong

# make ests long - jttp
jttpSenateEsts %>% 
  select(Rate:jumpXTransTrip, maxConv, sim) %>% 
  gather(parameter, estimate, Rate:jumpXTransTrip) -> melt1 
jttpSenateEsts %>% 
  select(se_density:maxConv, sim) %>% 
  gather(parameter, se, se_density:se_jumpXTransTrip) %>% 
  mutate(parameter = str_replace(parameter, "se_", "")) -> melt2 
left_join(melt1, melt2) %>% arrange(sim) -> jttpSenLong

# make ests long - jtts
jttsSenateEsts %>% 
  select(Rate:jumpXTransTrip, maxConv, sim) %>% 
  gather(parameter, estimate, Rate:jumpXTransTrip) -> melt1 
jttsSenateEsts %>% 
  select(se_density:maxConv, sim) %>% 
  gather(parameter, se, se_density:se_jumpXTransTrip) %>% 
  mutate(parameter = str_replace(parameter, "se_", "")) -> melt2 
left_join(melt1, melt2) %>% arrange(sim) -> jttsSenLong

>>>>

```{r M1, echo = FALSE, message=FALSE,warning=FALSE}
